\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{hyperref}

% Title Page
\title{Software Development Project - 1DV600 - Test documentation}
\author{Claes Weyde \\ 
	e-mail: \href{mailto:cw222av@student.lnu.se}{cw222av@student.lnu.se} \\
	github: \href{https://github.com/Cosbus/cw222av_1dv600_}{https://github.com/Cosbus/\texttt{cw222av\_1dv600\_}}}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{The Marvelous Hanging Man - Test documentation}
\fancyhead[L]{Claes Weyde}
\fancyfoot[C,C]{\leftmark}
\fancyfoot[L]{\thepage}
\fancyfoot[R]{Version 1.0}



\begin{document}
\maketitle
\newpage
\tableofcontents{}
\newpage

\section{Test Plan}

\subsection{Objectives}
\subsection{To-do}
\begin{itemize}
	\item Plan work
	\begin{itemize}
		\item Is required functionality missing?
		\item Should new functionality be implemented?
		\item Prioritize what needs to be done.
	\end{itemize}
	\item Update project document.
	\item Possible: Implement new features.
	\begin{itemize}
		\item Prepare UML for new features.
		\item Implement new features.
		\item Test new features as well as whole game.
	\end{itemize}
	\item Complete and hand in project.
\end{itemize}
\subsection{Time estimates and Time log}
\begin{center}
	\begin{tabular}{|c|c|c|} 
		\hline
		Task & Estimate [hrs] & Actual time \\ [0.5ex] 
		\hline\hline
		Plan work & 2 & -- \\ 
		\hline
		Document update & 1 & --\\
		\hline 
		Possible implementation & 10-15 & -- \\ 
		\hline
		Finish up and hand in & 2 & --\\ 
		\hline 
		Total time & 20 & --\\ [1ex]
		\hline
		
	\end{tabular}
\end{center}
\newpage
\section{Manual test cases}
\subsection{Manual tests of Play Game main scenario}
\subsubsection{TC 2.2 - Successfully providing a correct letter}
\begin{itemize}
	\item Name: Successfully providing a correct letter.
	\item Test case ref: TC 2.2
	\item Use case ref: UC 2.3
	\item Description: The test case tests how the system responds when the user provides a letter which is correct, and the word is not completely solved.
\end{itemize}
\emph{Input}
\begin{enumerate}
	\item \underline{Precondition:} The user has started the game.
	\item Test case TC 2.1. choose "play game" from main menu.
	\item Input a correct letter.
	\item Press enter.
\end{enumerate}
\emph{Output}
\begin{itemize}
	\item The system prints "Correct!" on the screen.
	\item The system prints the number of letters remaining on the screen.
	\item The system prints the number of tries remaining on the screen.
	\item The system prompts the user to enter a new letter by printing "Please provide a letter:" on the screen.
\end{itemize}
\emph{Comments}
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\subsubsection{TC 2.3 - Providing an incorrect letter}
\begin{itemize}
	\item Name: Providing an incorrect letter.
	\item Test case ref: TC 2.3
	\item Use case ref: UC 2.3.1
	\item Description: The test case tests how the system responds when the user provides a letter which is incorrect, and the user has more tries.
\end{itemize}
\emph{Input}
\begin{enumerate}
	\item \underline{Precondition:} The user has started the game.
	\item Test case TC 2.1. choose "play game" from main menu.
	\item Input an incorrect letter.
	\item Press enter.
\end{enumerate}
\emph{Output}
\begin{itemize}
	\item The system prints "Unfortunately wrong." on the screen.
	\item The system prints the number of letters remaining on the screen.
	\item The system prints the number of tries remaining on the screen.
	\item The system prompts the user to enter a new letter by printing "Please provide a letter:" on the screen.
\end{itemize}
\emph{Comments}
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\subsubsection{TC 2.6 - Returning from play to main menu}
\begin{itemize}
	\item Name: Returning from play to main menu.
	\item Test case ref: TC 2.6
	\item Use case ref: UC 2.7
	\item Description: The test case tests how the system responds when the user has finished a word (either by finding the word or having exhausted his/hers amount of tries) and chooses to return to the main menu.
\end{itemize}
\emph{Input}
\begin{enumerate}
	\item \underline{Precondition:} The user has finished a word and the system has provided the user with the choice of returning to main menu, playing a new word or quitting the game altogether.
	\item Finish a word.
	\item Input "m" to return to main menu.
	\item Press enter.
\end{enumerate}
\emph{Output}
\begin{itemize}
	\item The system shows the main menu on the screen.
\end{itemize}
\emph{Comments}
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\end{document}          
